An enhancer code compendium of early human neural and neural crest development

### 2025-04-25 manuscript.tex
M&M: cryosectioning

\paragraph*{\textit{ex ovo} enhancer-reporter injection}
Preparation of chicken embryos and injection was performed as described in Williams and Sauka-Spengler 2021\cite{
williamsExOvoElectroporation2021}.
Eggs were incubated as described above (see Chicken embryos). A hole was created in the egg shell using the back of
foreceps, thick albumin was discarded and thin albumin was collected. When most albumin was removed, the egg shell was
cut open and yolk turned so that embryo faces upwards. More albumin was removed from the yolk by stroking the yolk using
serrated forceps, moving away from (and not touching) the embryo. A Whatman filter paper with perforated hole was placed
on top of the embryo and yolk and whatman paper was cut using dissection scissors and embryo was removed and placed in
Ringer solution 
(
  $NaCl_2$ \SI{62.5}{\micro\molar}; 
  KCl \SI{5}{\micro\molar}; 
  $CaCl_2\cdot2H_2O$ \SI{1.5}{\micro\molar};
  $NaHPO_4\cdot7H_2O$ \SI{0.75}{\micro\molar};
  $KH_2PO_4$ \SI{0.15}{\micro\molar}
).
Embryo was placed in custom elektroporation cuvette (see Williams and Sauka-Spengler 2021\cite{
williamsExOvoElectroporation2021}), enhancer-reporter plasmid mixture (
enhancer-reporter plasmid \SI{2}{\micro\gram\per\micro\litre};
injection control plasmid \SI{1}{\micro\gram\per\micro\litre};
food coloring
) was injected using micro injector in the cavity between the blastoderm and underlying viteline membrane and
embryo was elektroorated (5 pules of 5V: 100 ms on, 50 ms off). Embryo was grown for 24 hours at \SI{37}{\degreeCelsius}
and imaged whole mount

>>>>

\paragraph*{\textit{ex ovo} enhancer-reporter injection}
Preparation of chicken embryos and injection was performed as described in Williams and Sauka-Spengler 2021\cite{
williamsExOvoElectroporation2021}.
Eggs were incubated as described above (see Chicken embryos). A hole was created in the egg shell using the back of
foreceps, thick albumin was discarded and thin albumin was collected. When most albumin was removed, the egg shell was
cut open and yolk turned so that embryo faces upwards. More albumin was removed from the yolk by stroking the yolk using
serrated forceps, moving away from (and not touching) the embryo. A Whatman filter paper with perforated hole was placed
on top of the embryo and yolk and whatman paper was cut using dissection scissors and embryo was removed and placed in
Ringer solution 
(
  $NaCl_2$ \SI{62.5}{\micro\molar}; 
  KCl \SI{5}{\micro\molar}; 
  $CaCl_2\cdot2H_2O$ \SI{1.5}{\micro\molar};
  $NaHPO_4\cdot7H_2O$ \SI{0.75}{\micro\molar};
  $KH_2PO_4$ \SI{0.15}{\micro\molar}
).
Embryo was placed in custom elektroporation cuvette (see Williams and Sauka-Spengler 2021\cite{
williamsExOvoElectroporation2021}), enhancer-reporter plasmid mixture (
enhancer-reporter plasmid \SI{2}{\micro\gram\per\micro\litre};
injection control plasmid \SI{1}{\micro\gram\per\micro\litre};
food coloring
) was injected using micro injector in the cavity between the blastoderm and underlying viteline membrane and
embryo was elektroorated (5 pules of 5V: 100 ms on, 50 ms off). Embryo was grown for 24 hours at \SI{37}{\degreeCelsius}
and imaged whole mount or sectioned and imaged.

\paragraph*{Chicken embryo cryosectioning}
Embryos were fixed in \SI{4}{\percent} paraformaldehyde for 1 hour at room temperature followed by three 
10 minutes washes with PBS. 
Embryos were transferred to \SI{15}{\percent} V/V sucrose in PBS at room temperature until they sank to the bottom. 
Next, embryos were transferred to a mixture consiting of \SI{7.5}{\percent} V/V gelatin and \SI{15}{\percent} V/V 
sucrose in PBS and were incubated overnight at \SI{37}{\degreeCelsius}. 
In the meantime \SI{20}{\percent} V/V gelatin was dissolved in PBS at \SI{60}{\degreeCelsius} and this was kept at 
\SI{37}{\degreeCelsius} once the gelatin was dissolved. 
After the overnight incubating, embryos were transferred to the gelatin solution and kept for a minimum of 4 hours at 
\SI{37}{\degreeCelsius}. 
Finally, embryos in gelatin solution were transferred to a cryomold and quickly frozen on an aluminum block cooled by 
dry ice.
Cryosections of \SI{20}{\micro\meter} were made at \SI{-14}{\degreeCelsius} and collected on SuperFrost Plus Adhesion 
slides (Fisher Scientific, 10149870). 
Sections were stained with DAPI (\SI{0.1}{\milli\gram\per\milli\litre} in PBS; Sigma-Aldrich, 28718-90-3) 
for 15 minutes, followed by a PBS wash and air dried. Cover slip was mounted using Mowiol 4-88 mounting medium
(Sigma-Aldrich, 81381-50G).
